---
title: "formative.rmd"
author: "Jiusi Xu"
date: "October 5, 2017"
output: html_document
---

```{r}
install.packages("dplyr")
library(dplyr)

```

How many people enrolled in HarvardX/CS50x recieved certification in 2012? 

```{r}
d1<-read.csv("HMXPC13_DI_v2_5-14-14.csv")
d2<-filter(d1,certified=="1")
d3<-dplyr::filter(d2, grepl('HarvardX/CS50x', course_id))
count(d3,certified)   

```

How many people registered for HarvardX/CS50x from Columbia on October 15, 2012?

```{r}
d4<-filter(d1,start_time_DI=="2012-10-15")  #people who registered on 2012/10/15
d5<-filter(d4,final_cc_cname_DI=="Columbia")   #people who are from Columbia and registered on 2012/10/15

count(d5)
count(d4)

#I got 0 results in d5. I checked the original data and I found people from Columbia. It should not be 0 results.
```

Create a new data frame (D2) that includes student ID and registration date for all students from a country of your choice

```{r}
d6<-filter(d1,final_cc_cname_DI=="Japan") #students from Japan
D2<-select(d6,start_time_DI,userid_DI)

```

Create a new data frame (D3) in which the column names are the registration dates, with one column containing the student ids and all other cells indicating a 1 if the student registered on that date or an NA if they did not

```{r}
d7<-select(d1,start_time_DI,userid_DI)
matching<-as.numeric(d7$start_time_DI %in% D2$start_time_DI)
D3<-cbind(d7,matching)
D3[D3 == 0] <- NA

```

Now make the row names of D3 the student ids on your new data frame and remove the user id column from your data frame

```{r}
d8<-D3
D3<-select(d8,-2)
names(D3)<-c("Registration Dates","Registered")

```

Convert your data frame to a matrix (M1)

```{r}
M1<-data.matrix(D3)

```

Create a new matrix which is the transposed version of your matrix (M2)

```{r}
M2<-t(M1)

```

Create a third matrix (M3) that is a student by student matrix where the cells in the matrix represent if two studentes registered on the same day (This will take a lot of processing power, you may not be able to complete it if you have a large number of students)


```{r}
M3<- M1 %*% M2
```

Convert the diagonal of your matrix into NAs

```{r}
diag(M2)<-NA

```
